How to compute the fusion product of MV cycles in type A

### 2021-02-21 draft.tex
added picture of T plus defense of argument

\acom{Roger and I have been using $\ast$ to denote fusion. Do we need a notation for the scheme-theoretic closure of $X_1\times X_2\times\AA^\times$? If not then I like $X_1\ast X_2 = \overline{X_1 \times X_2 \times \AA^\times}\cap \pi^{-1}(0)$.}
\jcom{I think that we will need notations for both things, but I'm happy to use $ \ast$ for the central fibre and use something else for the whole family.} \acom{Ok, I have changed it to notation from Roger's thesis/AK. Only now I am confused as to what is being called fusion---why do we not take the top dimensional subscheme?}
\jcom{I guess that there are two things that one could mean by fusion of MV cycles.  This scheme $ X_1 \circ X_2$ or the expression which appear in Theorem 7.11 of mvbasis, which is a linear combination of the top-dimensional components of this scheme with multiplicites.  In the general context of this section ($X_1, X_2$ are not necessarily MV cycles), then I guess it is best to talk about the subscheme.  Maybe we can call the expression appearing Theorem 7.11 the ``numerical fusion'' of MV cycles.  By the way, somewhere in this paper we should explain Theorem 7.11 and say that this gives us motivation to study fusion of MV cycles.}

@@

\begin{itemize}
    \item For $ s \in \CC$, we have a Jordan form matrix $ J_{s,\lambda}$ with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$. \acom{$s\in\AA$?}
    % 
    \item The adjoint orbit $ \OO^\lambda \subset M_N(\CC)$ of matrices conjugate to $ J_{0,\lambda}$.  Its closure is $ \overline{\OO}^\lambda = \bigcup_{\lambda' \le \lambda} \OO^{\lambda'}$.
    % 
    \item For $ s \in \CC, s \ne 0$, the adjoint orbit $ \OO^{\lambda_1, \lambda_2}_{0,s}$ of matrices conjugate to $ J_{0,\lambda_1} \oplus J_{s,\lambda_2}$.  Its closure is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s} = \bigcup_{\lambda_1' \le \lambda_1, \lambda'_2 \le \lambda_2} \OO^{\lambda_1', \lambda'_2}_{0,s}$. \acom{$s\in\AA$?}
    % 
    \item A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space $V$ is said to have Jordan type $((0,\lambda_1), (s,\lambda_2))$ if its matrix representatives lie in $ \OO^{\lambda_1, \lambda_2}_{0,s}$.
    % 
    \item The family of adjoint orbits $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,\AA} \rightarrow \AA$ whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s}$ and whose fibre over 0 is $\overline{\OO}^\lambda$.  \jcom{We should justify why the 0 fibre is correct scheme-theoretically.} 
    \acom{does it follow because ``$s$ divides $\det g$'' is a closed condition 
    in $\AA_s\times \AA_{\det}$? 
    so the set of $A$ which are conjugate to
    $J_{0,\lambda_1} \oplus J_{s,\lambda_2}$
    by a matrix whose determinant is divisible by $s$ is also closed?}
    \jcom{I didn't follow your argument. One approach would be to write down the generators for the ideal of $overline{\OO}^{\lambda_1, \lambda_2}_{0,s} $ and then set $ s =0$.  For example, take $ \lambda_1 = (1) = \lambda_2 $ (I know it is a small example!), then the ideal is generated by $ tr(A) = s$, $det(A) = 0$, so when we take $ s =0$, we get just $ tr(A) = 0, det(A) = 0$.  I am hoping that we can find a reference for this result somewhere.}

    \item Fix the ``\mu-numeration'' \((e^1_1,\ldots,e^{\mu_1}_1,\ldots,e^1_m,\ldots,e^{\mu_m}_m)\) of the standard basis of $\CC^N$. The Mirkovic--Vybnornov slice $\TT_\mu$ is defined as the set of $A\in M_N(\CC)$ such that 
    \[
        \begin{aligned}
            &\text{for all } 1 \le a,s\le m\,,
            \text{for all } 1\le b\le \mu_a\,, 1\le t\le \mu_s\,, \\
            &\text{if } 1\le t < \mu_s \text{ or } t = \mu_s < b \le \mu_a \\
            &\text{then } (e^t_s)' (A-J_\mu) e^b_a = 0 \,.
        \end{aligned}    
    \]
    In words, $A$ is a $\mu\times\mu$ block matrix with possibly nonzero entries occuring in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block. 
    Mirkovic and Vybornov describe $\TT_\mu$ as the slice in which $f$ acts as close to regular nilpotent as possible.
    % $\dim \TT_\mu = N^2 - \dim \OO_\mu$. 
    \acom{this ok?} % \jcom{Anne, can you add this definition?}
    \jcom{When you wrote ``In words,'', it is not quite correct because of the diagonal blocks have those 1s.  Also it would be good to have an example.  And what is $f$ in the last sentence? }

@@

    \acom{Maybe $\UU$ for a different letter? And, I guess we do not need $\AA$ but it is a nice letter to have around. It also serves to distinguish the $\CC$ over which $R,K$ are defined from the $\AA$ over which $\Grbd$ is defined?}
    \jcom{Sure $\UU$ is good.}
\end{itemize}

@@

\jcom{Do we have a reference?}

@@

\section{Denouement}

>>>>

\acom{Roger and I have been using $\ast$ to denote fusion. Do we need a notation for the scheme-theoretic closure of $X_1\times X_2\times\AA^\times$? If not then I like $X_1\ast X_2 = \overline{X_1 \times X_2 \times \AA^\times}\cap \pi^{-1}(0)$.}
\jcom{I think that we will need notations for both things, but I'm happy to use $ \ast$ for the central fibre and use something else for the whole family.} \acom{Ok, I have changed it to notation from Roger's thesis/AK. Only now I am confused as to what is being called fusion---why do we not take the top dimensional subscheme?}
\jcom{I guess that there are two things that one could mean by fusion of MV cycles.  This scheme $ X_1 \circ X_2$ or the expression which appear in Theorem 7.11 of mvbasis, which is a linear combination of the top-dimensional components of this scheme with multiplicites.  In the general context of this section ($X_1, X_2$ are not necessarily MV cycles), then I guess it is best to talk about the subscheme.  Maybe we can call the expression appearing Theorem 7.11 the ``numerical fusion'' of MV cycles.  By the way, somewhere in this paper we should explain Theorem 7.11 and say that this gives us motivation to study fusion of MV cycles.}
\acom{Sure! It is quoted at the end, in \Cref{s:denouement} as an application.}

@@

\begin{itemize}
    \item For $ s \in \CC$, we have a Jordan form matrix $ J_{s,\lambda}$ with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$. \acom{$s\in\AA$?}
    % 
    \item The adjoint orbit $ \OO^\lambda \subset M_N(\CC)$ of matrices conjugate to $ J_{0,\lambda}$.  Its closure is $ \overline{\OO}^\lambda = \bigcup_{\lambda' \le \lambda} \OO^{\lambda'}$.
    % 
    \item For $ s \in \CC, s \ne 0$, the adjoint orbit $ \OO^{\lambda_1, \lambda_2}_{0,s}$ of matrices conjugate to $ J_{0,\lambda_1} \oplus J_{s,\lambda_2}$.  Its closure is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s} = \bigcup_{\lambda_1' \le \lambda_1, \lambda'_2 \le \lambda_2} \OO^{\lambda_1', \lambda'_2}_{0,s}$. \acom{$s\in\AA$?}
    % 
    \item A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space $V$ is said to have Jordan type $((0,\lambda_1), (s,\lambda_2))$ if its matrix representatives lie in $ \OO^{\lambda_1, \lambda_2}_{0,s}$.
    % 
    \item The family of adjoint orbits $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,\AA} \rightarrow \AA$ whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s}$ and whose fibre over 0 is $\overline{\OO}^\lambda$.  \jcom{We should justify why the 0 fibre is correct scheme-theoretically.} 
    \acom{does it follow because ``$s$ divides $\det g$'' is a closed condition 
    in $\AA_s\times \AA_{\det}$? 
    so the set of $A$ which are conjugate to
    $J_{0,\lambda_1} \oplus J_{s,\lambda_2}$
    by a matrix whose determinant is divisible by $s$ is also closed?}
    \jcom{I didn't follow your argument. One approach would be to write down the generators for the ideal of $\overline{\OO}^{\lambda_1, \lambda_2}_{0,s} $ and then set $ s =0$.  For example, take $ \lambda_1 = (1) = \lambda_2 $ (I know it is a small example!), then the ideal is generated by $ tr(A) = s$, $det(A) = 0$, so when we take $ s =0$, we get just $ tr(A) = 0, det(A) = 0$.  I am hoping that we can find a reference for this result somewhere.}
    \acom{I thought that the point would be to show that a dense subset of matrices which are conjugate to $J_{0,\lambda_1}\oplus J_{s,\lambda_2}$ limit to matrices which are conjugate to $J_\lambda$. In particular, that the conjugating matrix remains invertible in the $s\to0$ limit.}

    \item Fix the ``\mu-numeration'' \((e^1_1,\ldots,e^{\mu_1}_1,\ldots,e^1_m,\ldots,e^{\mu_m}_m)\) of the standard basis of $\CC^N$. The Mirkovic--Vybnornov slice $\TT_\mu$ is defined as the set of $A\in M_N(\CC)$ such that 
    \[
        \begin{aligned}
            &\text{for all } 1 \le a,s\le m\,,
            \text{for all } 1\le b\le \mu_a\,, 1\le t\le \mu_s\,, \\
            &\text{if } 1\le t < \mu_s \text{ or } t = \mu_s < b \le \mu_a \\
            &\text{then } (e^t_s)' (A-J_\mu) e^b_a = 0 \,.
        \end{aligned}    
    \]
    In words, $A$ is a $\mu$ Jordan form matrix plus a $\mu\times\mu$ block matrix with possibly nonzero entries occuring in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block. 
    Mirkovic and Vybornov describe $\TT_\mu$ as the slice in which $f$ acts as close to regular nilpotent as possible.
    % $\dim \TT_\mu = N^2 - \dim \OO_\mu$. 
    In pictures, the elements $A$ look like 
    \[
        \left[\begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c}
             & 1 & & & & & \\
             &  & 1 & & & & \\
            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
              &  & &  & 1 & & \\
              A_{21}^1 & A_{21}^2 & & A_{22}^1 & A_{22}^2 & A_{23}^1 & A_{24}^1 \\
             A_{31}^1 & & & A_{32}^1 & & A_{33}^1 & A_{34}^1 \\
             A_{41}^1 & & & A_{42}^1 & & A_{43}^1 & A_{43}^1
        \end{BMAT}
        \right]
    \]
    % 
    \acom{this ok?} % \jcom{Anne, can you add this definition?}
    \jcom{When you wrote ``In words,'', it is not quite correct because of the diagonal blocks have those 1s.  Also it would be good to have an example.  And what is $f$ in the last sentence? }
    \acom{fixed? As for $f$ I think it is an $\sl_2$ triplet. Hopeful you could explain what MVy meant bc I never quite understood!}

@@

    \acom{Maybe $\UU$ for a different letter? And, I guess we do not need $\AA$ but it is a nice letter to have around. It also serves to distinguish the $\CC$ over which $R,K$ are defined from the $\AA$ over which $\Grbd$ is defined?}
    \jcom{Sure $\UU$ is good.}
    \acom{And, sorry, ignore my other comment; it's the same $\CC$ (or $\AA$) nothing to distinguish.}
\end{itemize}

@@

\jcom{Do we have a reference?}
\acom{Your paper with Sabin??}

@@

\section{Denouement}
\label{s:denouement}
